A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-11-02 ms.tex
conc end

We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx 150~\textrm{Myr}$, heliocentric distance $D \approx 30~\kpc$, and metallicity $\feh \approx -1.1$.
At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys will provide many more [...].

>>>>

We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx 150~\textrm{Myr}$, heliocentric distance $D \approx 30~\kpc$, and metallicity $\feh \approx -1.1$.
At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys provides a wealth of information about our Galaxy and stellar halo.
